\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2023-02-26 Latex/paper.tex
# add \sim
# last version on the paper

In order to have a Markovian representation of the HJM, we will assume that the volatility is separable, i.e.
\begin{equation}
\sigma(t,T)= h(t)g(T).
\end{equation}
with $g$ a positive time-dependent function and $h$ a non-negative process. In addition
\begin{align*}
\eta_t &= g(t)h(t,x_t,y_t)  \nonumber \\
k_t &= - \frac{\partial_t g(t)}{g(t)}.
\end{align*}
Throught this paper, we assume the following hypotheses on $\eta(t,x,y)$.
\begin{hypothesis}\label{boundedness_volatility} 
The process $\eta_t$ is global Lipschitz and differentiable a.s. In addition, we will suppose that
\begin{align*}
\alpha_1 \leq \eta(t,x,y) \leq \alpha_2 \quad \forall (t,x,y) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+}. \\
|\eta(t,x_2,y_2) - \eta(t,x_1,y_1)| \leq C_{x,y} \lVert (x_2-x_1,y_2-y_1)\rVert \quad \forall (t,x,y) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+} 
\end{align*}
with $\lVert \cdot \rVert$ euclidean norm in $\mathbb{R}^{2}$.
\end{hypothesis}
\begin{hypothesis}\label{boundedness_reversion} 
The mean reversion function $k(\cdot)$ is positive a.s.
\end{hypothesis}
\begin{remark}
Notice that the above hypotheses have been chosen for the sake of simplicity, but they can be replaced by adequate integrability conditions.
\end{remark}
We must note, that under the hypothesis (\ref{boundedness_volatility}) $\partial_x \eta(t,x,y)$ and $\partial_y \eta(t,x,y)$ are bounded. This version of the HJM is also known as the Cheyette model, \cite{Cheyette}. It is easy to show (see \cite{Andreasen01} that
\begin{equation}
r_{ois}(t)=f_{ois}(t,t)= f_{ois}(0,t) + x_t,
\end{equation}  
where
\begin{align}\label{short_rate_cheyette}
dx_t &= (-k_t x_t + y_t)dt + \eta(t,x_t,y_t) dW_t^{\mathbb{Q}} \nonumber \\
dy_t &= (\eta^{2}_t - 2 k_t y_t) dt ,
\end{align} 
with 
\begin{align*}
\eta_t &= g(t)h(t,x_t,y_t)  \nonumber \\
k_t &= - \frac{\partial_t g(t)}{g(t)}.
\end{align*}
Now if we do a little bit of algebra and we use Itô formula we can show the next representation formula for $P_{ois}(t,T)$
\begin{equation}\label{bond_ois}
P_{ois}(t,T) = \frac{P_{ois}(0,T)}{P_{ois}(0,t)} \exp\left(-G(t,T)x_t - \frac{1}{2} G^{2}(t,T)y_t \right)
\end{equation}
where $G(t,T) = \int_{t}^{T} \exp\left(-\int_{t}^{u} k_s ds \right) du$. We must observe, that under the representation (\ref{estimation_forward_rate_curve}) we have that
\begin{equation}\label{bond_forward}
P_{E}(t,T)=H(t,T)P_{ois}(t,T)
\end{equation}
where $H(t,T)=\exp\left(-\int_{t}^{T}s(t,u) du \right)$.

@@

\begin{example}\label{example_ca_future}
Let us to set 
\begin{align*}
g(T) &= \exp(-kT) \\
h(t) &= \sigma
\end{align*}
\end{example}
With this parametrization, the Cheyette model is equiavalent to Hull-White model. Also, from the definition of $g(\cdot)$ and $h(\cdot)$, we have that
\begin{align*}
\eta_s &= \sigma \exp(-ks)\\
\beta(s,u, x_0, \bar{y}_s) &= \sigma \exp(-ku) \\
\nu(s,t_2) &= \sigma \frac{\exp(-ks) - \exp(-kt_2)}{k}\\
\end{align*}
Then it easy to show that the convexity adjustment (\ref{ca_approximation_futures}) is
\begin{align*}
CA(t_0,t_1) & \approx \frac{\sigma^{2} \exp(-k t_0)  P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\frac{1 - \exp(- k t_0)}{k^{2}} - \frac{t_0 \exp(-k t_2)}{k} \right).   
\end{align*}
\newpage
In the next figure, we can check the accuracy of the last formula versus montecarlo. The parameters that we have used are $\sigma=0.015$, $k=0.003$ and flat curve with level $r=0.01$.

@@

\subsection{FRAs in arrears}
The price of a FRA in arrears, is the most classic example between the porducts with convexity adjustment. The cash flows associated to a FRAs in arrears is $L_{E}(t_1,t_1,t_2)$ in $t_1$. Therefore the payment will be
\begin{equation}
P_{E}(0,t_1)\mathbb{E}^{\mathbb{Q}^{t_1}}\left( L_{E}(t_1,t_1,t_2\right).
\end{equation}
The expected value is clearly taken with respect to the wrong martingale, because $L_{E}(t,t_1,t_2)$ is martingale under the measure $\mathbb{Q}^{t_2}$. In order to calculate, the convexity adjustment we will use as before Clark-Ocone to get a representation for $L_{E}(t_1,t_1,t_2)$ i.e
\begin{equation}\label{general_convexity_fras}
L_{E}(t_1,t_1,t_2) = \mathbb{E}^{\mathbb{Q}^{t_2}}\left(L_{E}(t_1,t_1,t_2) \right) + \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}
\end{equation}
The if we suppose the HJM dynamic (\ref{estimation_forward_rate_curve})and we take $\mathbb{E}^{^{\mathbb{Q}^{t_1}}}(\cdot)$ we get
\begin{align*}
\mathbb{E}^{\mathbb{Q}^{t_1}}\left(L_{E}(t_1,t_1,t_2) \right) &= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}\right)\\
&= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) (\nu(s,t_2)-\nu(s,t_1)) ds \right)
\end{align*}
Where we have used that 
\begin{equation*}
dW^{\mathbb{Q}^{t_2}}_s = dW^{\mathbb{Q}^{t_1}}_s + (\nu(s,t_2) - \nu(s,t_1)) ds 
\end{equation*}
Now from (\ref{approximation_D_s_x_t}) we have that 
\begin{equation*}
D_s L(t_1,t_1,t_2) = \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(t_1,t_2)} D_s x_{t_1} \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, x_0, \bar{y}_s)\bar{M}(s,t_1)
\end{equation*}
Therefore, if we define and we use (\ref{approsimation_E_s_x_t}) we have that
\begin{equation*}
CA(t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( L_{E}\left(t_1,t_1,t_2\right)\right) - L_{E}\left(0,t_1,t_2\right)
\end{equation*}
and we use the last approximation and (\ref{general_convexity_fras}), we can get the next approximation for $CA(t_0,t_1)$ 
\hspace{2cm}
\fboxsep1em
\fbox{\parbox{475pt}
{
\begin{equation}\label{ca_approximations_fra_arrears}
CA(t_0,t_1) \approx  \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \int_{0}^{t_1} \beta(s,t_1, x_0, \bar{y}_s) \exp\left(-\int_{s}^{t_1} \partial_x \beta(u,t_1,x_0,y_0) \nu(u,t_2) du \right) (\nu(s,t_2) - \nu(s,t_1)) ds.
\end{equation}
}}
\begin{example}
To check how works the last approximation. We will restrict a Hull-White model with mean reversion and volatility constant. We will use are $\sigma=0.1$, $k=0.007$ for our model. The analytical approximation that we get from (\ref{ca_approximation_futures}) is
\begin{equation*}
CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \exp(- k(t_1 + u)) -   \exp(- k(t_2 + u)) du 
\end{equation*}
We have checked the last approximation using MC method to compute the value of a FRA in arrears. We will show the result of the simulation in the next figure

@@

\section{Order of the approximation $\bar{x}_t$}
From (\ref{short_rate_cheyette}) is easy to show that
\begin{equation*}
x_{t_a} = \int_{0}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du^{\prime}\right) G(u,t_a) \eta^{2}(u,x_u,y_u) du + \int_{0}^{t_a}  \exp\left(-\int_{u}^{t_a}k_u^{\prime} du \right) \eta(u,x_u,y_u) dW_u^{\mathbb{Q}} 
\end{equation*}
Therefore, we have that
\begin{align*}
(x_{t_a} - \bar{x}_{t_a})^2 &\leq 2 \left(\int_{0}^{t_a} \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) G(u,t_a) (\eta^{2}(u,x_u,y_u) - \eta^{2}(u,x_0,y_0)) du \right)^{2} \\ 
&+ 2 \left(\int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u^{\prime} du^{\prime} \right) (\eta(u,x_u,y_u)-\eta(u,\bar{x}_u,\bar{y}_u)) dW_u^{\mathbb{Q}}\right)^{2}
\end{align*}
Now, we will bound each integral term. We will call to the first term $(A)$ and the second $(B)$. From the hypothesis (\ref{boundedness_volatility}) we have that 
\begin{align*}
(A) &\leq 8 t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \|(x_u -x_0,y_u-y_0)\|^{2} du \\
&\leq 16 t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \|(x_u - \bar{x}_u,y_u-\bar{y}_u)\|^{2} du \\
&+ 16 t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \|(\bar{x}_u - x_0,\bar{y}_u-y_0)\|^{2} du
\end{align*}
and we take $\mathbb{E}^{\mathbb{Q}}\left(\cdot\right)$ on above inequality
\begin{align*}
\mathbb{E}^{\mathbb{Q}}\left((A)\right) &\leq 16  t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{s}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \mathbb{E}^{\mathbb{Q}}\left(\|(\bar{x}_u -x_0,\bar{y}_u-y_0)\|^{2}\right) du \\
&+\leq 16  t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{s}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \mathbb{E}^{\mathbb{Q}}\left(\|(x_u - \bar{x}_u,y_u-\bar{y}_u)\|^{2}\right) du
\end{align*}
Again, from the hypotheses (\ref{boundedness_volatility}) and (\ref{boundedness_reversion}) we can show that 
\begin{equation*}
\mathbb{E}^{\mathbb{Q}}\left(\|(\bar{x}_u -x_0,\bar{y}_u-y_0)\|^{2}\right) = K h(u)
\end{equation*}
where $K$ is a constant with no dependency in $u$ and $h(u)\sim \mathcal{O}(u)$. In order to bound $(B)$, we will use the Doob's inequality and (\ref{boundedness_volatility}). Then
\begin{align*}
\mathbb{E}^{\mathbb{Q}}&\left((B)\right) \leq 2K \int_{0}^{t_a}  \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime} \right) (\eta(u,x_u,y_u)-\eta(u,\bar{x}_u,\bar{y}_u))^{2} du \\
& \leq 2K C^{2}_{x,y} \int_{0}^{t_a}  \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime} \right) \mathbb{E}^{\mathbb{Q}}\left(\|(x_u - \bar{x}_u, y_u - \bar{y}_u) \|^{2}\right) du
\end{align*}
On other hand, we have that
\begin{equation*}
\mathbb{E}^{\mathbb{Q}}\left((y_{t_a} - \bar{y}_{t_a})^{2} \right) \leq 4 \alpha^{2}_{2} C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right)\mathbb{E}^{\mathbb{Q}}\left(\|(x_u-\bar{x}_u,y_u-\bar{y}_u)\|^{2}\right) du    
\end{equation*}
Now, if we put all of the above together, we get that
\begin{equation*}
\mathbb{E}^{\mathbb{Q}}\left(\|(x_{t_a} - \bar{x}_{t_a},y_{t_a} - \bar{y}_{t_a})\|^{2}\right) \leq C_1H(t_a) + C_2\int_{0}^{t_a} \mathbb{E}^{\mathbb{Q}}\left(\|(x_{u} - \bar{x}_{u},y_{u} - \bar{y}_{u})\|^{2}\right) du
\end{equation*}
where $H(t_a) \mathcal{O}(t_a)$. To end, if we apply the Gronwall's lemma we have that
\begin{equation*}
\mathbb{E}^{\mathbb{Q}}\left(\|(x_{t_a} - \bar{x}_{t_a},y_{t_a} - \bar{y}_{t_a})\|^{2}\right) \leq C_1H(t_a) \exp\left(C_2 t_a\right)
\end{equation*}

>>>>

In order to have a Markovian representation of the HJM, we will assume that the volatility is separable, i.e.
\begin{equation}
\sigma(t,T)= h(t)g(T).
\end{equation}
with $g$ a positive time-dependent function and $h$ a non-negative process. In addition
\begin{align*}
\eta_t &= g(t)h(t,x_t,y_t)  \nonumber \\
k_t &= - \frac{\partial_t g(t)}{g(t)}.
\end{align*}
Throught this paper, we assume the following hypotheses on $\eta(t,x,y)$.
\begin{hypothesis}\label{boundedness_volatility} 
The process $\eta_t$ is global Lipschitz and differentiable a.s. In addition, we will suppose that
\begin{align*}
\alpha_1 \leq \eta(t,x,y) \leq \alpha_2 \quad \forall (t,x,y) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+}. \\
|\eta(t,x_2,y_2) - \eta(t,x_1,y_1)| \leq C_{x,y} \lVert (x_2-x_1,y_2-y_1)\rVert \quad \forall (t,x,y) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+} 
\end{align*}
with $\lVert \cdot \rVert$ euclidean norm in $\mathbb{R}^{2}$.
\end{hypothesis}
\begin{hypothesis}\label{boundedness_reversion} 
The mean reversion function $k(\cdot)$ is a continuous and positive a.s such that
\begin{equation*}
m_k < k(t) \leq M_k \quad \forall t \geq 0.
\end{equation*}

\begin{remark}
Under these assumptions on $k(\cdot)$, we have that
\begin{equation*}
\lim_{t \to \infty}  I(\alpha,0,t):= \lim_{t \to \infty} \int_{0}^{t} \exp\left(-\alpha \int_{u}^{t} k(s) ds\right) du \leq \frac{1}{\alpha m_k} \quad \text{with} \quad \alpha > 0.
\end{equation*}
On other hand, as well it is easy to show that
\begin{equation*}
\lim_{t \to \infty}  J(\alpha,0,t):= \lim_{t \to \infty} \int_{0}^{t} G^{\alpha}(u,t) \exp\left(-\alpha \int_{u}^{t} k(s) ds\right) du \leq \frac{1}{\alpha m^{\alpha+1}_{k}}
\end{equation*}
\end{remark}

\end{hypothesis}
\begin{remark}
Notice that the above hypotheses have been chosen for the sake of simplicity, but they can be replaced by adequate integrability conditions.
\end{remark}
We must note, that under the hypothesis (\ref{boundedness_volatility}) $\partial_x \eta(t,x,y)$ and $\partial_y \eta(t,x,y)$ are bounded. This version of the HJM is also known as the Cheyette model, \cite{Cheyette}. It is easy to show (see \cite{Andreasen01} that
\begin{equation}
r_{ois}(t)=f_{ois}(t,t)= f_{ois}(0,t) + x_t,
\end{equation}  
where
\begin{align}\label{short_rate_cheyette}
dx_t &= (-k_t x_t + y_t)dt + \eta(t,x_t,y_t) dW_t^{\mathbb{Q}} \nonumber \\
dy_t &= (\eta^{2}_t - 2 k_t y_t) dt ,
\end{align} 
with 
\begin{align*}
\eta_t &= g(t)h(t,x_t,y_t)  \nonumber \\
k_t &= - \frac{\partial_t g(t)}{g(t)}.
\end{align*}
Now if we do a little bit of algebra and we use Itô formula we can show the next representation formula for $P_{ois}(t,T)$
\begin{equation}\label{bond_ois}
P_{ois}(t,T) = \frac{P_{ois}(0,T)}{P_{ois}(0,t)} \exp\left(-G(t,T)x_t - \frac{1}{2} G^{2}(t,T)y_t \right)
\end{equation}
where $G(t,T) = \int_{t}^{T} \exp\left(-\int_{t}^{u} k_s ds \right) du$. We must observe, that under the representation (\ref{estimation_forward_rate_curve}) we have that
\begin{equation}\label{bond_forward}
P_{E}(t,T)=H(t,T)P_{ois}(t,T)
\end{equation}
where $H(t,T)=\exp\left(-\int_{t}^{T}s(t,u) du \right)$.

@@

\begin{example}\label{example_ca_future}
Let us to set 
\begin{align*}
g(T) &= \exp(-kT) \\
h(t) &= \sigma
\end{align*}
\end{example}
With this parametrization, the Cheyette model is equiavalent to Hull-White model. Also, from the definition of $g(\cdot)$ and $h(\cdot)$, we have that
\begin{align*}
\eta_s &= \sigma \exp(-ks)\\
\beta(s,u, x_0, \bar{y}_s) &= \sigma \exp(-ku) \\
\nu(s,t_2) &= \sigma \frac{\exp(-ks) - \exp(-kt_2)}{k}\\
\end{align*}
Then it easy to show that the convexity adjustment (\ref{ca_approximation_futures}) is
\begin{align*}
CA(t_0,t_1) & \approx \frac{\sigma^{2} \exp(-k t_0)  P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\frac{1 - \exp(- k t_0)}{k^{2}} - \frac{t_0 \exp(-k t_2)}{k} \right).   
\end{align*}

In the next figure, we can check the accuracy of the last formula versus montecarlo. The parameters that we have used are $\sigma=0.015$, $k=0.003$ and flat curve with level $r=0.01$.

@@

\newpage
\subsection{FRAs in arrears}
The price of a FRA in arrears, is the most classic example between the porducts with convexity adjustment. The cash flows associated to a FRAs in arrears is $L_{E}(t_1,t_1,t_2)$ in $t_1$. Therefore the payment will be
\begin{equation}
P_{E}(0,t_1)\mathbb{E}^{\mathbb{Q}^{t_1}}\left( L_{E}(t_1,t_1,t_2\right).
\end{equation}
The expected value is clearly taken with respect to the wrong martingale, because $L_{E}(t,t_1,t_2)$ is martingale under the measure $\mathbb{Q}^{t_2}$. In order to calculate, the convexity adjustment we will use as before Clark-Ocone to get a representation for $L_{E}(t_1,t_1,t_2)$ i.e
\begin{equation}\label{general_convexity_fras}
L_{E}(t_1,t_1,t_2) = \mathbb{E}^{\mathbb{Q}^{t_2}}\left(L_{E}(t_1,t_1,t_2) \right) + \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}
\end{equation}
The if we suppose the HJM dynamic (\ref{estimation_forward_rate_curve})and we take $\mathbb{E}^{^{\mathbb{Q}^{t_1}}}(\cdot)$ we get
\begin{align*}
\mathbb{E}^{\mathbb{Q}^{t_1}}\left(L_{E}(t_1,t_1,t_2) \right) &= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}\right)\\
&= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) (\nu(s,t_2)-\nu(s,t_1)) ds \right)
\end{align*}
Where we have used that 
\begin{equation*}
dW^{\mathbb{Q}^{t_2}}_s = dW^{\mathbb{Q}^{t_1}}_s + (\nu(s,t_2) - \nu(s,t_1)) ds 
\end{equation*}
Now from (\ref{approximation_D_s_x_t}) we have that 
\begin{equation*}
D_s L(t_1,t_1,t_2) = \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(t_1,t_2)} D_s x_{t_1} \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, x_0, \bar{y}_s)\bar{M}(s,t_1)
\end{equation*}
Therefore, if we define and we use (\ref{approsimation_E_s_x_t}) we have that
\begin{equation*}
CA(t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( L_{E}\left(t_1,t_1,t_2\right)\right) - L_{E}\left(0,t_1,t_2\right)
\end{equation*}
and we use the last approximation and (\ref{general_convexity_fras}), we can get the next approximation for $CA(t_0,t_1)$ 
\hspace{2cm}
\fboxsep1em
\fbox{\parbox{475pt}
{
\begin{equation}\label{ca_approximations_fra_arrears}
CA(t_0,t_1) \approx  \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \int_{0}^{t_1} \beta(s,t_1, x_0, \bar{y}_s) \exp\left(-\int_{s}^{t_1} \partial_x \beta(u,t_1,x_0,y_0) \nu(u,t_2) du \right) (\nu(s,t_2) - \nu(s,t_1)) ds.
\end{equation}
}}
\begin{example}
To check how works the last approximation. We will restrict a Hull-White model with mean reversion and volatility constant. We will use are $\sigma=0.1$, $k=0.007$ for our model. The analytical approximation that we get from (\ref{ca_approximation_futures}) is
\begin{equation*}
CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \exp(- k(t_1 + u)) -   \exp(- k(t_2 + u)) du 
\end{equation*}
We have checked the last approximation using MC method to compute the value of a FRA in arrears. We will show the result of the simulation in the next figure

@@

\section{Order of the approximation $\bar{x}_t$}
From (\ref{short_rate_cheyette}) is easy to show that
\begin{equation*}
x_{t_a} = \int_{0}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du^{\prime}\right) G(u,t_a) \eta^{2}(u,x_u,y_u) du + \int_{0}^{t_a}  \exp\left(-\int_{u}^{t_a}k_u^{\prime} du \right) \eta(u,x_u,y_u) dW_u^{\mathbb{Q}} 
\end{equation*}
Therefore, we have that
\begin{align*}
(x_{t_a} - \bar{x}_{t_a})^2 &\leq 2 \left(\int_{0}^{t_a} \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) G(u,t_a) (\eta^{2}(u,x_u,y_u) - \eta^{2}(u,x_0,y_0)) du \right)^{2} \\ 
&+ 2 \left(\int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u^{\prime} du^{\prime} \right) (\eta(u,x_u,y_u)-\eta(u,\bar{x}_u,\bar{y}_u)) dW_u^{\mathbb{Q}}\right)^{2}
\end{align*}
Now, we will bound each integral term. We will call to the first term $(A)$ and the second $(B)$. From the hypothesis (\ref{boundedness_volatility}) we have that 
\begin{align*}
(A) &\leq 8 t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \|(x_u -x_0,y_u-y_0)\|^{2} du \\
&\leq 16 t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \|(x_u - \bar{x}_u,y_u-\bar{y}_u)\|^{2} du \\
&+ 16 t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \|(\bar{x}_u - x_0,\bar{y}_u-y_0)\|^{2} du
\end{align*}
and we take $\mathbb{E}^{\mathbb{Q}}\left(\cdot\right)$ on above inequality
\begin{align*}
\mathbb{E}^{\mathbb{Q}}\left((A)\right) &\leq 16  t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \mathbb{E}^{\mathbb{Q}}\left(\|(\bar{x}_u -x_0,\bar{y}_u-y_0)\|^{2}\right) du \\
&+\leq 16  t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \mathbb{E}^{\mathbb{Q}}\left(\|(x_u - \bar{x}_u,y_u-\bar{y}_u)\|^{2}\right) du
\end{align*}
Again, from the hypotheses (\ref{boundedness_volatility}) and (\ref{boundedness_reversion}) we can show that 
\begin{equation*}
\mathbb{E}^{\mathbb{Q}}\left(\|(\bar{x}_u -x_0,\bar{y}_u-y_0)\|^{2}\right) \sim \mathcal{O}(I(0,u,2))
\end{equation*}
In order to bound $(B)$, we will use the Doob's inequality and (\ref{boundedness_volatility}). Then
\begin{align*}
\mathbb{E}^{\mathbb{Q}}&\left((B)\right) \leq 2K \int_{0}^{t_a}  \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime} \right) (\eta(u,x_u,y_u)-\eta(u,\bar{x}_u,\bar{y}_u))^{2} du \\
& \leq 2K C^{2}_{x,y} \int_{0}^{t_a}  \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime} \right) \mathbb{E}^{\mathbb{Q}}\left(\|(x_u - \bar{x}_u, y_u - \bar{y}_u) \|^{2}\right) du
\end{align*}
On other hand, we have that
\begin{equation*}
\mathbb{E}^{\mathbb{Q}}\left((y_{t_a} - \bar{y}_{t_a})^{2} \right) \leq 4 \alpha^{2}_{2} C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right)\mathbb{E}^{\mathbb{Q}}\left(\|(x_u-\bar{x}_u,y_u-\bar{y}_u)\|^{2}\right) du    
\end{equation*}
Now, if we put all of the above together, we get that
\begin{equation*}
\mathbb{E}^{\mathbb{Q}}\left(\|(x_{t_a} - \bar{x}_{t_a},y_{t_a} - \bar{y}_{t_a})\|^{2}\right) \leq C_1H(t_a) + C_2\int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime} \right) \mathbb{E}^{\mathbb{Q}}\left(\|(x_{u} - \bar{x}_{u},y_{u} - \bar{y}_{u})\|^{2}\right) du
\end{equation*}
where $C_1$ and $C_1$ are adequate positive constants and $H(t_a) \sim \mathcal{O}(\int_{0}^{t_a} I(0,u,2) du)$. To end, if we apply a slightly modified version of the Gronwall's lemma we have that
\begin{equation*}
\mathbb{E}^{\mathbb{Q}}\left(\|(x_{t_a} - \bar{x}_{t_a},y_{t_a} - \bar{y}_{t_a})\|^{2}\right) \leq C_1 H(t_a)+ \int_{0}^{t_a} \exp\left(- C_2 \int_{u}^{t} k(s^{\prime})  ds^{\prime} \right) H(u) du.
\end{equation*}
